Basic Analysis of Simplex output

### 2015-11-01 tools/analyses/Rmd/BasicAnalysis.Rmd

```{r, results = 'hide', echo=T, message = F, warning = F}
# A table where each columns corresponds to a state variable or model output.  
simplex.dat <- read.csv("~/GitHub/simplex/results/simulated_data/examples/SimData.csv")
simplex.dat$h.tau <- log((simplex.dat$width * simplex.dat$height)/simplex.dat$flow.rate)

# Replacing 0's with 1's to allow log-transforms below
simplex.dat$total.abundance[simplex.dat$total.abundance<=0] <- 1
simplex.dat$N.max[simplex.dat$N.max<=0] <- 1
simplex.dat$species.richness[simplex.dat$species.richness<=0] <- 1
simplex.dat$resource.particles[simplex.dat$resource.particles<=0] <- 1
simplex.dat$resource.concentration[simplex.dat$resource.concentration<=0] <- 1

simplex.dat$total.abundance <- log(simplex.dat$total.abundance)
simplex.dat$N.max <- log(simplex.dat$N.max)
simplex.dat$species.richness <- log(simplex.dat$species.richness)
simplex.dat$resource.particles <- log(simplex.dat$resource.particles)
simplex.dat$resource.concentration <- log(simplex.dat$resource.concentration)
simplex.dat[is.na(simplex.dat)] <- 0
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}

# Physical and metacommunity variables
phys.dat <- as.matrix(subset(simplex.dat, 
                      select = c(h.tau,
                                 flow.rate,
                                 barriers,
                                 width,
                                 height,
                                 amplitude,
                                 frequency,
                                 phase)))

scatterplotMatrix(phys.dat, main="Physical data", diagonal = "none")
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
# Resource variables
res.dat <- as.matrix(subset(simplex.dat, 
                      select = c(resource.concentration,
                      shannons.resource.diversity,
                      resource.richness,
                      resource.particles)))

scatterplotMatrix(res.dat, main="Resource data", diagonal = "none")
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
# Physiological variables
physio.dat <- as.matrix(subset(simplex.dat, 
                      select = c(biomass.prod.N,
                      biomass.prod.C,
                      biomass.prod.P,
                      avg.per.capita.N.efficiency,
                      avg.per.capita.P.efficiency,
                      avg.per.capita.C.efficiency,
                      max.growth.rate,
                      max.met.maint)))

scatterplotMatrix(physio.dat, main="Physiological data", diagonal = "none")
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
diversity.dat <- as.matrix(subset(simplex.dat, 
                      select = c(total.abundance,
                      N.max,
                      species.richness,
                      simpson.e,
                      e.var,
                      Whittakers.turnover,
                      Jaccards.dissimilarity)))

scatterplotMatrix(diversity.dat, main="Diversity data", diagonal = "none")
```

>>>>

```{r, results = 'hide', echo=T, message = F, warning = F}
# A table where each columns corresponds to a state variable or model output.  
simplex.dat <- read.csv("~/GitHub/simplex/results/simulated_data/examples/SimData.csv")

# Replacing 0's with 1's to allow log-transforms below
simplex.dat <- simplex.dat[complete.cases(simplex.dat), ]

simplex.dat$total.abundance[simplex.dat$total.abundance<=0] <- 0.00001
simplex.dat$N.max[simplex.dat$N.max<=0] <- 0.00001
simplex.dat$species.richness[simplex.dat$species.richness<=0] <- 0.00001
simplex.dat$resource.particles[simplex.dat$resource.particles<=0] <- 0.00001
simplex.dat$resource.concentration[simplex.dat$resource.concentration<=0] <- 0.00001
simplex.dat$Whittakers.turnover[simplex.dat$Whittakers.turnover<=0] <- 0.00001
simplex.dat$Jaccards.dissimilarity[simplex.dat$Jaccards.dissimilarity<=0] <- 0.00001

simplex.dat$total.abundance <- log(simplex.dat$total.abundance)
simplex.dat$N.max <- log(simplex.dat$N.max)
simplex.dat$Whittakers.turnover <- log(simplex.dat$Whittakers.turnover)
simplex.dat$Jaccards.dissimilarity <- log(simplex.dat$Jaccards.dissimilarity)
simplex.dat$species.richness <- log(simplex.dat$species.richness)
simplex.dat$resource.particles <- log(simplex.dat$resource.particles)
simplex.dat$resource.concentration <- log(simplex.dat$resource.concentration)

```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
# Physical and metacommunity variables
png(filename="~/GitHub/simplex/results/figures/examples/PhysicalUnivariate.png")

phys.dat <- as.matrix(subset(simplex.dat, 
                      select = c(flow.rate,
                                 barriers,
                                 width,
                                 height,
                                 amplitude)))

scatterplotMatrix(phys.dat, main="Physical data", diagonal = "none")
dev.off()
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
# Resource variables
png(filename="~/GitHub/simplex/results/figures/examples/ResourceUnivariate.png")

res.dat <- as.matrix(subset(simplex.dat, 
                      select = c(resource.concentration,
                      shannons.resource.diversity,
                      resource.richness,
                      resource.particles)))

scatterplotMatrix(res.dat, main="Resource data", diagonal = "none")
dev.off()
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
# Physiological variables
png(filename="~/GitHub/simplex/results/figures/examples/PhysioUnivariate.png")

physio.dat <- as.matrix(subset(simplex.dat, 
                      select = c(biomass.prod.N,
                      avg.per.capita.N.efficiency,
                      max.growth.rate,
                      max.met.maint)))

scatterplotMatrix(physio.dat, main="Physiological data", diagonal = "none")
dev.off()
```

@@

```{r, results='hide', echo=T, message=F, warning=F, fig.width=7, fig.height=6}
# Diversity-related variables
png(filename="~/GitHub/simplex/results/figures/examples/DiversityUnivariate.png")

diversity.dat <- as.matrix(subset(simplex.dat, 
                      select = c(total.abundance,
                      N.max,
                      species.richness,
                      simpson.e,
                      Whittakers.turnover,
                      Jaccards.dissimilarity)))

scatterplotMatrix(diversity.dat, main="Diversity data", diagonal = "none")
dev.off()
```
